---
title: "Understanding Hotstar’s Content Dynamics: Production Trends by Genre, Type, and Age Rating"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This analysis delves into the content dynamics of Hotstar, one of the leading streaming platforms. By examining a dataset comprising various titles available on Hotstar, this study aims to uncover key patterns and trends in content production. The analysis focuses on understanding the distribution of different content types, such as movies and TV shows, and explores how genres and running times vary across different age ratings. Additionally, it identifies the most and least common genres, highlights the titles with the longest and shortest durations, and provides insights into the production trends over the years. This comprehensive overview offers valuable insights into Hotstar’s content strategy, catering to diverse audiences and shaping its offerings in the competitive streaming landscape.

## Including Code

You can include R code in the document as follows:

```{r}
# Clear the environment
rm(list = ls())

# Load necessary packages and install if not already installed
required_packages <- c("Hmisc", "dplyr", "ggplot2", "tidyr")

for (pkg in required_packages) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  }
}

# Read the CSV file (update the path as per your local setup)
data <- read.csv("~/Data Analysis/hotstar.csv")

# Duplicate the 'seasons' and 'episodes' columns and replace NAs with 1
data <- data %>%
  mutate(
    seasons_dup = ifelse(is.na(seasons), 1, seasons),
    episodes_dup = ifelse(is.na(episodes), 1, episodes)
  )

# Display the first few rows of the modified data
head(data)
```

## Optionally describe the updated data

```{r}
describe(data)
```

```{r}
# 1. Determine which type has comparatively high production
production_summary <- data %>%
  group_by(type) %>%
  summarize(Count = n()) %>%
  arrange(desc(Count))

```

# Plot production by type

```{r , echo=FALSE}
ggplot(production_summary, aes(x = reorder(type, -Count), y = Count, fill = type)) +
  geom_bar(stat = "identity") +
  labs(title = "Production by Type", x = "Type", y = "Count") +
  theme_minimal()
```

# 2. Identify titles with the highest and lowest running time

```{r}
running_time_summary <- data %>%
  filter(!is.na(running_time)) %>%
  arrange(running_time)
```

# Display titles with highest and lowest running time

```{r}
highest_running_time <- tail(running_time_summary, 1)
lowest_running_time <- head(running_time_summary, 1)

print("Title with the Highest Running Time:")
print(highest_running_time)

print("Title with the Lowest Running Time:")
print(lowest_running_time)

# Plot running time by genre instead of title
data_separated <- data %>%
  separate_rows(genre, sep = ",") %>%
  group_by(genre) %>%
  summarize(
    max_running_time = ifelse(all(is.na(running_time)), NA, max(running_time, na.rm = TRUE)),
    min_running_time = ifelse(all(is.na(running_time)), NA, min(running_time, na.rm = TRUE))
  ) %>%
  arrange(desc(max_running_time))
```

```{r , echo=FALSE}
# Remove rows with missing running time before plotting
cleaned_data <- data_separated %>%
  filter(!is.na(max_running_time) & !is.na(min_running_time))

# Plot with replaced missing values
ggplot(cleaned_data, aes(x = reorder(genre, -max_running_time), y = max_running_time)) +
  geom_point(color = "blue") +
  labs(title = "Maximum Running Time by Genre", x = "Genre", y = "Running Time (minutes)") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), # Rotate x-axis labels
    plot.margin = margin(t = 10, r = 10, b = 20, l = 10) # Add margin (top, right, bottom, left)
  )
```

# 3. Show the number of movies or TV shows produced each year

```{r}
yearly_production <- data %>%
  filter(!is.na(year)) %>%
  group_by(year, type) %>%
  summarize(Count = n(), .groups = 'drop')
```

# Plot production by year

```{r , echo=FALSE}
ggplot(yearly_production, aes(x = year, y = Count, color = type)) +
  geom_line() +
  labs(title = "Number of Movies/TV Shows Produced Each Year", x = "Year", y = "Count") +
  theme_minimal()
```

# 4. Count the number of titles by genre

```{r}
genre_count <- data %>%
  separate_rows(genre, sep = ",") %>%
  group_by(genre) %>%
  summarize(Count = n()) %>%
  arrange(desc(Count))
```

```{r , echo=FALSE}
# Plot number of titles by genre
ggplot(genre_count, aes(x = reorder(genre, -Count), y = Count, fill = genre)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Titles by Genre", x = "Genre", y = "Count") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8), # Adjust text size and position
    plot.margin = margin(5, 5, 20, 5)  # Increase the bottom margin to provide space
  )
```

# 5. Find the title with the maximum seasons

```{r}
max_seasons_title <- data %>%
  filter(!is.na(seasons)) %>%
  arrange(desc(seasons)) %>%
  slice(1)  # Get the first row with the maximum seasons

# Display the title with maximum seasons
print("Title with the Maximum Seasons:")
print(max_seasons_title)
```

# 6. Find the title with the maximum episode

```{r}
max_episode_title <- data %>%
  filter(!is.na(episodes_dup)) %>%
  arrange(desc(episodes_dup)) %>%
  slice(1)  # Get the first row with the maximum episode

# Display the title with maximum episdoe
  print("Title with the Maximum Seasons:")
  print(max_episode_title)
```

# 7.Count the number of titles by genre for each age rating

```{r}
  genre_age_rating <- data %>%
  separate_rows(genre, sep = ",") %>%
  group_by(age_rating, genre) %>%
  summarize(Count = n(), .groups = 'drop') %>%  
  arrange(age_rating, desc(Count))
  
  # Display the summarized data
  print(genre_age_rating)
```

```{r , echo=FALSE}
  # Plot number of titles by genre for each age rating
  ggplot(genre_age_rating, aes(x = reorder(genre, -Count), y = Count, fill = age_rating)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = "Number of Titles by Genre and Age Rating", x = "Genre", y = "Count") +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
      plot.margin = margin(5, 5, 20, 5)
    )
  

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
